### 2020-08-10 S2_appendix.tex
results update

\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{array}
\usepackage{mhchem}
\usepackage{mathtools}

@@

Every method presented and tested in this paper was validated with a well-calibrated simulation study using the same model and operator set that which was benchmarked. This is achieved using 100 simulated datasets (each with $N=100$ taxa and a $L=5000$ nt alignment). The 95 \% highest posterior density (HPD) interval is calculated, and the `true' parameter values are compared with their values estimated from the simulated data.

The validation results are presented as plots. The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95 \% HPD interval. If all parameters have coverage close to 95 \% coverage, then this suggests correctness of implementation.

The parameters presented in each plot are: the Yule model birth rate $\lambda$, rate heterogeneity gamma shape $\Gamma$, HKY substitution model parameter $\kappa$, log-normal clock standard deviation $\sigma$, the frequency of the A nucleotide $f_A$, and the rate of the first taxon $r_1$. The remaining 3 frequencies and 99 taxa rates are omitted from the figures.

\begin{figure}[!htb]
\includegraphics[width=0.85\textwidth]{Figures/CalSim_cat.pdf}
\caption{\textbf{The \textit{cat} parameterisation.} Blue and red vertical lines are 95 \% HPD intervals, where blue intervals contain the true value and red intervals do not.}
\label{fig:rateparams}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.85\textwidth]{Figures/CalSim_real.pdf}
\caption{\textbf{The \textit{real} parameterisation,} with the operators decribed by Zhang and Drummond 2020.}
\label{fig:rateparams}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.85\textwidth]{Figures/CalSim_quant.pdf}
\caption{\textbf{The \textit{quant} parameterisation,} with the operators decribed by Zhang and Drummond 2020, and adapted for \textit{quant} as described in \textbf{S1 Appendix}.}
\label{fig:rateparams}
\end{figure}

\bibliography{references}

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{array}
\usepackage{mhchem}
\usepackage{mathtools}

@@

The methods presented and benchmarked in this paper were validated with well-calibrated simulation studies using the same model and operator scheme that was benchmarked. 
This was achieved using 100 simulated datasets (each with $N=30$ taxa and a $L=2000$ nt alignment).
The 95\% highest posterior density (HPD) intervals of each parameter during MCMC were calculated, and these intervals were compared with the `true' parameter values which the data was simulated under.

The validation results are presented as plots (below). 
In each plot, blue and red vertical lines are 95\% HPD intervals, where blue intervals contain the true value and red intervals do not.
The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95\% HPD interval. 
If all parameters have coverage close to 95\%, then this suggests correctness of both methodology and implementation.

Overall, these experiments suggest that the operators presented in the main paper were correctly implemented.

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{Figures/N30_cat_adaptive.pdf}
\caption{\textbf{The adapt (\textit{cat}) configuration.} }
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{Figures/N30_real_adaptive.pdf}
\caption{\textbf{The adapt (\textit{real}) configuration.} }
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{Figures/N30_quant_cached_adaptive.pdf}
\caption{\textbf{The adapt (\textit{quant}) configuration.} The constant distance operators were extended from \emph{real} to \emph{quant} as described in \textbf{S1 Appendix}.}
\end{figure}

\begin{figure}[!htb]
%\includegraphics[width=\textwidth]{Figures/CalSim_NER_real.pdf}
\caption{\textbf{The Narrow Exchange Rate operators under the \textit{real} parameterisation.} The 48 NER and 48 NERw operators, including \texttt{NarrowExchange}, are tested in the same MCMC session.}
\end{figure}

\begin{figure}[!htb]
%\includegraphics[width=\textwidth]{Figures/CalSim_NER_quant.pdf}
\caption{\textbf{The \texttt{LeafAVMVN} configuration.} The adaptive NER operator, Bactrian proposals, and the \emph{real} configuration are included.}
\end{figure}

%\bibliography{references}

### 2020-08-10 S3_appendix.tex
results update

\section*{S2 Appendix: Well-calibrated simulation studies}

The methods presented and benchmarked in this paper were validated with well-calibrated simulation studies using the same model and operator scheme that was benchmarked. 
This was achieved using 100 simulated datasets (each with $N=30$ taxa and a $L=2000$ nt alignment).
The 95\% highest posterior density (HPD) intervals of each parameter during MCMC were calculated, and these intervals were compared with the `true' parameter values which the data was simulated under.

The validation results are presented as plots (below). 
In each plot, blue and red vertical lines are 95\% HPD intervals, where blue intervals contain the true value and red intervals do not.
The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95\% HPD interval. 
If all parameters have coverage close to 95\%, then this suggests correctness of both methodology and implementation.

Overall, these experiments suggest that the operators presented in the main paper were correctly implemented.

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{Figures/N30_cat_adaptive.pdf}
\caption{\textbf{The adapt (\textit{cat}) configuration.} }
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{Figures/N30_real_adaptive.pdf}
\caption{\textbf{The adapt (\textit{real}) configuration.} }
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{Figures/N30_quant_cached_adaptive.pdf}
\caption{\textbf{The adapt (\textit{quant}) configuration.} The constant distance operators were extended from \emph{real} to \emph{quant} as described in \textbf{S1 Appendix}.}
\end{figure}

\begin{figure}[!htb]
%\includegraphics[width=\textwidth]{Figures/CalSim_NER_real.pdf}
\caption{\textbf{The Narrow Exchange Rate operators under the \textit{real} parameterisation.} The 48 NER and 48 NERw operators, including \texttt{NarrowExchange}, are tested in the same MCMC session.}
\end{figure}

\begin{figure}[!htb]
%\includegraphics[width=\textwidth]{Figures/CalSim_NER_quant.pdf}
\caption{\textbf{The \texttt{LeafAVMVN} configuration.} The adaptive NER operator, Bactrian proposals, and the \emph{real} configuration are included.}
\end{figure}

>>>>

\section*{S3 Appendix: Supplementary results}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_catquant.pdf}
\caption{\textbf{Round 1: Performance evaluation of \texttt{AdaptiveOperatorSampler} under the \emph{quant} and \emph{cat} parameterisations.}
These results show that neither \emph{cat} nor \emph{quant} benefit strongly from adaptive weight sampling. The constant distance operators (cons) greatly improves the \emph{quant} parameterisation for most datasets, as expected. }
\end{figure}
